cardinalR: Generating interesting high-dimensional data structures

### 2025-04-20 paper-cardinalR.Rmd
Added missing citations

The paper is organized as follows. In next section, introduces the implementation of `cardinalR` package on CRAN and GitHub, including demonstration of the package's key functions. We illustrate how a clustering data structure affect the Non-linear dimension reductions in **Application** section. Finally, we give a brief conclusion of the paper and discuss potential opportunities for use of our data collection.

@@

# Examples

@@

This article is created using \CRANpkg{knitr} [@knitr] and \CRANpkg{rmarkdown} [@rmarkdown] in R with the `rjtools::rjournal_article` template.

>>>>

The paper is organized as follows. In next section, introduces the implementation of `cardinalR` package on CRAN and GitHub, including demonstration of the package's key functions. We illustrate how a clustering data structure affect the Non-linear dimension reductions in **Example** section. Finally, we give a brief conclusion of the paper and discuss potential opportunities for use of our data collection.

@@

# Example

@@

This article is created using \CRANpkg{knitr} [@yihui2015] and \CRANpkg{rmarkdown} [@yihui2018] in R with the `rjtools::rjournal_article` template.
